\chapter{Discussion}
\section{Determining the index of refraction}
This experiment has a lot of glaring issues. First of all, we measure two different indices of refraction dependent on which medium the light is refracted into, $1.503\pm0.012$ for glass to air and $1.427\pm 0.014$ for air to glass (see figure \ref{fig:new_weighted_average}). The two confidenceintervals are disjunct, so we would normally reject the hypothesis that they come from the same distribution.
This tells us that there must be something wrong with the angles measured, as this is the only thing our calculation of the refractive index depends on. 
One obvious problem is the spreading of the light. 
This is a problem with our setup, as we must have used the lenses wrong. 
The lens was supposed to focus the beam, but we were not able to place the lens at the correct distance from the sensor, 
because arm the sensor was on, was too short (see figure \ref{fig:SensorSetup}).
Other problems could be that the semicircle was not centered correctly, 
such that the laser would move thorugh its center. 
We made sure to place the semicircle such that it was in the center, 
but it was not fixed on the rotation platform on which it rested, 
so it could potentially have moved.
% [rp, tp, rs, ts]
% [1.30429486 1.30429135 1.30429637 1.30428983]
% sigma**2 [0.00056172, 0.00056074, 0.00056159, 0.00056087]
On top of measuring two different indices of refraction from the use of Snell's law, we also measure a third index, 
a unanimous $n = 1.3$ we get from fitting the Fresnel equations to our data. It is weird however, because if we plot the Fresnel equations using the other indices, 
it seems to fit better (figure \ref{fig:fresnell_comparison}), as there are obvious systematic deviations at large $\theta_i$ in the s polarisation case. 
We also know that glass has a refractive index around 1.4\autocite{polyanskiy_refractiveindex} (assuming it is made of BK7, a common glasstype used in optics), which further discredits the fit (it is however equally far away from our measurements of 1.5 in the case of glass to air, yet quite close to the 1.427 measured in air to glass, and we also don't know if the glass really is made of BK7, so this is really not a meaningful comparison).
Because of all these different values we have to conclude that we have been unable to determine the refractive index,
and that we would need to redo this part of the experiment.

\section{The Fresnel Equations}
There was also the issue that a significant portion of the light disappeared somewhere, 
as we noticed that $R + T$ was alot lower than 1 (see figure \ref{fig:bad_fresnel_comparison}) when we normalized using $V_0$.
We are unsure as to why this is, 
as it cannot only be a product of the large angle beam widening, because the dramatic intensity drop off happened at all angles.
It would therefore have to be the result of something else, 
maybe the glass that we used absorbed alot of the light, or the lens reflected some of it.

In spite of this, our model that the light decreased by a constant factor for both the reflected and transmitted light, 
led to great agreement between the expected and measured values, as can be seen in figure \ref{fig:fresnell_comparison}.
Of course, this is in part thanks to us forcing $R + T = 1$ by construction, but it does not force it to vary as a function of $\theta_i$ in the way it does, 
so this does still strongly support the validity of the Fresnel equations.

\section{Application of the Fresnel relations}
When would it be useful to understand the Fresnel relations? \newline
A real-world use would be using polarized \mbox{sunglasses}, when going fishing. 
With normal \mbox{sunglass} filters like neutral density filters of \mbox{different} types, you let both $s$- and $p$-polarized glare form the surface of the water pass to your eye.

A better option is to take advantage of the Fresnel relations to filter out the glare at angles $\le$ Brewster's angle \autocite{paschotta_brewster}.
For an air-to-water \mbox{interface}, Brewster's angle is $\approx 56^\circ$ and vertically polarized sunglasses can block out most of the glare dependent on the angle of the sun.
With most of the $s$-polarized reflected light blocked from you eye, you can see below the surface of the water.