\chapter{Discussion}
The results show that a linear model only gives a mediocre discription of the expansion of the piezoelectric actuator. 
This is expected as we know that piezoelectric materials often does not have a linear expansion. 
The difference in the fits and the data indicate that we have hysteresis. 
The presens of hysteresis means that the expansion is not only dependant on the voltage but also the ealier state of the system. 

The experiments with higher order polynomials show that the data in some cases can be fitted better.
But it is not the underlying problem. 
The third degree model probably introduced overfitting without giving any meaningful description of the hysteresis.
The Second degree model gives better fits which suggests that there probably is som none linear behavior.
This is still is not enough to be a good model of the system since it still assumes a wrong connection between displacement and voltage.

A significant limit of the methods used is that the displacement is not messured directly but instead though measurements of intensities based on an interference model which introduces a lot of uncertaincies.
There was an attept to limit some of these. There was taken a messurement of the background intensity which was substracted from the data. 
There seemingly was a large error in splitting up the data through the voltage messurement from the function generator. 
In Figure $4$ we clearly see that the peak of decreasing and increasing intensity is not shared but is only the decent of the intensity. 
We do not have a good guess as to where this offset should come. It does not seem to be the code since many different tries yields the same result.
Even though this is a large benefactor as to why the result are not great, it does not help when we manually shifts the offset to accomodate for the error. 
There is also the error of the oscilloscopes voltage messurement, that is also present in the data. We clearly see the lines where the voltage jumps to the new messurement. 
This of cause is not ideal but seems negible to the other uncertaincies mentioned.

A better model could also have been used to analyse the data as the Preisach model or the Bouc-Wen model. 
